Single Cell Xenopus TMT Analysis

### 2020-02-23 Analysis.Rmd
added RMarkdown manuscript

---
title: "Single Cell Xenopus TMT Analysis"
author: "Kyle Kovary"
date: "5/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RColorBrewer)
library(pheatmap)
library(GGally)
library(VIM)
library(org.Xl.eg.db)
library(GO.db)
library(ggrepel)

@@

for(i in seq_along(files)){
  if(i == 1){
    rm(pepRaw)
  }
  if(!exists('pepRaw')){
    pepRaw = read_tsv(file = files[i]) %>% mutate(file = files[i], massID = 1:nrow(.))
  } else{
    temp = read_tsv(file = files[i]) %>% mutate(file = files[i], massID = 1:nrow(.))
    colnames(temp) = colnames(pepRaw)
    pepRaw = rbind(pepRaw, temp)
    rm(temp)
  }
}
pepRaw = pepRaw %>% dplyr::select(file, massID, everything()) %>% filter(!is.na(`126`), 
                                                                  `Quan Usage` == 'Use',
                                                                  Confidence != 'Low')

@@

mypal = rev(colorRampPalette(brewer.pal(11, 'RdBu'))(201))
k = NA
map = pheatmap(cor, show_colnames = F, show_rownames = F, color = mypal, breaks = seq(-1,1, by = 0.01), cutree_cols = k, cutree_rows = k, legend = F)
map
tibble(Uniprot = protImpute$Uniprot, Cluster = cutree(map$tree_row, k = k)) %>% write_csv('/Users/kylekovary/Downloads/Map.csv')

@@

```{r eval=F}
columns(org.Xl.eg.db)
mapIds(org.Xl.eg.db, keys = 'A0JPG5', keytype = 'UNIPROT', column = 'GOALL', multiVals = 'list')

@@

ggpairs(log2(glyc[,2:ncol(glyc),]))
```

@@

## All combinations of 5 proteins -> total error vs correlation
```{r}
combMat <- combn(1:length(cor))
corVect <- tibble(protA = rep(rownames(cor), times = length(colnames(cor))), 
                  protB = rep(colnames(cor), each = length(rownames(cor))),
                  keep = as.vector(lower.tri(cor)),
                  cor = as.vector(cor)) %>% filter(keep) %>% dplyr::select(-keep)

@@

## Variance within highly correlated GO terms
```{r}
allGO[grep('large ribo',allGO$GO),]
hCor <- filter(allGO, GOterms == 'GO:0015934')$Uniprot %>% unlist()

@@

ggplot(hCorSD, aes(x = sample, y = sd)) + geom_point() + geom_hline(yintercept = sd(hCor$abundance))
```

>>>>

---
title: "Single Cell Xenopus TMT Analysis"
author: "Kyle Kovary"
date: "5/15/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RColorBrewer)
library(pheatmap)
library(GGally)
library(VIM)
library(org.Xl.eg.db)
library(GO.db)
library(ggrepel)
library(plotly)

@@

for(i in seq_along(files)){
  if(i == 1 & exists('pepRaw')){
    rm(pepRaw)
  } else if(!exists('pepRaw')){
    pepRaw = read_tsv(file = files[i]) %>% mutate(file = files[i], massID = 1:nrow(.))
  } else{
    temp = read_tsv(file = files[i]) %>% mutate(file = files[i], massID = 1:nrow(.))
    colnames(temp) = colnames(pepRaw)
    pepRaw = rbind(pepRaw, temp)
    rm(temp)
  }
}
pepRaw <- pepRaw %>% dplyr::select(file, massID, everything()) %>% filter(!is.na(`126`), 
                                                                  `Quan Usage` == 'Use',
                                                                  Confidence != 'Low')

@@

mypal = rev(colorRampPalette(brewer.pal(11, 'RdBu'))(201))
k = 2
map = pheatmap(cor, show_colnames = F, show_rownames = F, color = mypal, breaks = seq(-1,1, by = 0.01), cutree_cols = k, cutree_rows = k, legend = F)
map

tibble(Uniprot = protImpute$Uniprot, Cluster = cutree(map$tree_row, k = k)) %>% write_csv('/Users/kylekovary/Downloads/Map.csv')

@@

```{r eval=F}
columns(org.Xl.eg.db)
#mapIds(org.Xl.eg.db, keys = 'A0JPG5', keytype = 'UNIPROT', column = 'GOALL', multiVals = 'list')

@@

#ggpairs(log2(glyc[,2:ncol(glyc),]))
```

@@

## All combinations of 5 proteins -> total error vs correlation
```{r}
combMat <- combn(1:length(colnames(cor)),2)
corVect <- tibble(protA = rep(rownames(cor), times = length(colnames(cor))), 
                  protB = rep(colnames(cor), each = length(rownames(cor))),
                  keep = as.vector(lower.tri(cor)),
                  cor = as.vector(cor)) %>% filter(keep) %>% dplyr::select(-keep)

@@

## Variance within highly correlated GO terms
```{r message=FALSE, warning=FALSE}
allGO[grep('large ribo',allGO$GO),]
hCor <- filter(allGO, GOterms == 'GO:0015934')$Uniprot %>% unlist()

@@

ggplot(hCorSD, aes(x = sample, y = sd)) + geom_point() + geom_hline(yintercept = sd(hCor$abundance))

BC_delta <- function(x) {
  hCor <- filter(allGO, GOterms == x)$Uniprot %>% unlist()

  hCor <- protImpute %>% filter(Uniprot %in% hCor) %>%
    mutate(symbol = mapIds(
      org.Xl.eg.db,
      keys = Uniprot,
      keytype = 'UNIPROT',
      column = 'SYMBOL'
    )) %>%
    dplyr::select(Uniprot, symbol, everything())

  hCor <- hCor %>% gather(key = sample, value = abundance, 3:ncol(hCor)) %>%
    dplyr::select(sample, symbol, abundance)

  return(hCorSD %>% summarise(sum(sd < sd(hCor$abundance)) / n()) %>% as.numeric())
}

dat <- dat %>% rowwise() %>% mutate(bcDelta = BC_delta(GOterms))

ggplot(dat, aes(x = medCors, y = bcDelta)) + geom_point(alpha = 0.5) + 
  geom_text_repel(data = filter(test, medCors > 0.2), 
                    aes(label = GO), colour = 'black', size = 2)
```
